Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-07-01 intro.tex
trivial tweak
update one reference

Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower the overall cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building supercomputers with millions of cores.
Even with such powerful networks, 
intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}.
%In order to explore the full potential of such powerful networks,  
%intelligent job placement is of paramount importance~\cite{bhatele2015, jain-sc14}.

@@

   \item Contiguous placement can be beneficial to the consistent performance of less communication-intensive applications by minimizing network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application. However, this comes with the downside of at times greatly reduced system performance via load imbalance.

>>>>

Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower the overall cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building supercomputers with millions of cores.
Even with such powerful networks, 
intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele:ipdps2016, jain-sc14}.
%In order to explore the full potential of such powerful networks,  
%intelligent job placement is of paramount importance~\cite{bhatele2015, jain-sc14}.

@@

   \item Contiguous placement can be beneficial to the consistent performance of less communication-intensive applications by minimizing network resource sharing, because it reduces the opportunities for traffic from other applications to be loaded on links that serve as minimal routes for the less intensive application. However, this comes with the downside of reduced system performance due to load imbalance.
